---
title: "BIOL432_Assignment1"
author: "Qiuhan Zhang"
date: "2023-01-13"
output: html_document
---

[My Github repository](https://github.com/qiuhan1008/BIOL432_Assignment1)

1. Load the revised measurements.csv

```{r}
#This measurement data includes 100 values for limb length and width, which were collected from 5 different species. 
mydata <- read.csv("measurements.csv")
```

```{r}
source("dataGenerato.R", local = knitr::knit_global())
source("volumeEstimato.R", local = knitr::knit_global())
```

2. Use dplyr to sort the data by species, then by observer, then by limb volume
```{r}
#load library
library(dplyr)
```

```{r}
data1 <- data1 %>% 
  arrange(organism, Observer, limb_volume) 
head(data1)
```


3. Create a table showing the average volume for each species
```{r}
avgvolume_data <- data1 %>%     
  group_by(organism) %>%
  summarise(Ave_volume = mean(limb_volume)) 
avgvolume_data
```


4. Create a table showing the number of observations (i.e. rows) for each combination of species and observer.
```{r}
observation_data <- data1 %>%     
  group_by(organism, Observer)  %>%     
  summarise(observations = n(), .groups = "drop") %>%  
  as.data.frame()
observation_data
```


5.Create a single box plot (or similar) to compare key features of the distributions of volumes for each species.
```{r}
#load ggplot
library(ggplot2)
```

```{r}
volume_plot <- ggplot(data1, 
                      aes(y = limb_volume, 
                          x = organism)) + 
  geom_boxplot() + 
  labs(x = "Species", 
       y = "Limb Volume")
volume_plot
```


6.Create a multi-panel plot showing frequency histograms showing the distribution of limb volume for each species. Note that this may require you to add code to you R markdown file to change the data from the wide to long format.
```{r}
volume_distribution <- ggplot(data1, 
       aes(x = limb_volume)) +
  geom_histogram() +
  facet_wrap(vars(organism)) + 
  labs(x = "Limb Volume", 
       y = "Frequency")
volume_distribution
```

